\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:01:54+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different predictive
probabilities on the data space. Two such models are also mutually
exclusive, $\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s
family distribution \emph{and} $M_{2}$'s family distribution at the same
time. It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant from this perspective. Some
authors try to define some \enquote{standard} distribution associated to a
family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.

Second, the \enquote{complexity} of a model cannot be judged from the
dimensionality of its family. Models $M_{1}$ and $M_{2}$ can have the same
family, but $M_{1}$ can have a family distribution concentrated on a very
small region, with respect to that of $M_{2}$. Model $M_{1}$ is thus
effectively using fewer parameters than $M_{2}$. Correspondingly the
\enquote{typical set} of data to which $M_{1}$ assigns appreciable
probability is smaller than the typical set of $M_{2}$: model $M_{1}$ is
less \enquote{powerful}. The effective dimensionality, complexity, or power
of a model is thus best defined by the volume of \emph{data space} that is
typical under that model. Most important, it may then happen that a model
is more powerful than another even if it is based on a lower-dimensional
family.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:05:53+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different predictive
probabilities on the data space. Two such models are also mutually
exclusive, $\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s
family distribution \emph{and} $M_{2}$'s family distribution at the same
time. It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant from this perspective. Some
authors try to define some \enquote{standard} distribution associated to a
family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. The
pre-data distribution over the family expresses our prior information and
is therefore highly dependent on the specific problem. Many such
\enquote{standard} distributions lead, moreover, to mathematical
singularities.

Second, the \enquote{complexity} of a model cannot be judged from the
dimensionality of its family. Models $M_{1}$ and $M_{2}$ can have the same
family, but $M_{1}$ can have a family distribution concentrated on a very
small region, with respect to that of $M_{2}$. Model $M_{1}$ is thus
effectively using a smaller parameter range than $M_{2}$. Correspondingly
the \enquote{typical set} of data to which $M_{1}$ assigns appreciable
probability is smaller than the typical set of $M_{2}$: model $M_{1}$ is
less \enquote{powerful}. The effective dimensionality, complexity, or power
of a model is thus best defined by the volume of \emph{data space} that is
typical under that model. Most important, it may then happen that a model
is more powerful than another even if it is based on a lower-dimensional
family.
